Universal Anonymous Signatures

### 2022-10-04 prism-backend/research/gsac/app-building-blocks.tex
Spellchecked full paper.

\begin{description}
\item[$\Eparm \gets \ESetup(\Esecpar)$.] Produces public parameters \Eparm given
  a security parameter \Esecpar.
\item[$(\Eek,\Edk) \gets \EKeyGen(\Eparm)$.] Given public parameters \Eparm,
  produces an encryption-decryption keypair $(\Eek,\Edk)$.
\item[$\Ec \gets \EEnc(\Eek,\msg)$.] Encrypts message \msg with encryption key
  \Eek, producing ciphertext \Ec.
\item[$\msg \gets \EDec(\Edk,\Ec)$.] Decrypts ciphertext \Ec with decryption key
  \Edk.
\end{description}

@@

Let \NIZKRel be an NP relation defined by pairs of elements $(\NIZKx,\NIZKw)$,
where \NIZKx is a statement and \NIZKw a witness proving that $(\NIZKx,\NIZKw)
\in \NIZKRel$. For concrete relations, we write $\NIZKRel = \lbrace (\NIZKx),
(\NIZKw): f(x,w) \rbrace$, where $f(x,w)$ is a boolean predicate denoting the
concrete conditions that \NIZKx and \NIZKw need to meet. The set of all \NIZKx
such that there exists a \NIZKw for which $(\NIZKx,\NIZKw) \in \NIZKRel$ is the
language, or \NIZKLang, for \NIZKRel. $\NIZKx \notin \NIZKLang$ means that
there is no $\NIZKw$ such that $(\NIZKx,\NIZKw) \in \NIZKRel$.

@@

When we want to make explicit the NP relation \NIZKRel to which the previous
algorithms refer to, we use $\NIZKSetup^\NIZKRel,\NIZKProve^\NIZKRel$, 
$\NIZKVerify^\NIZKRel$, etc., and omit the \NIZK prefix and superindex when
clear from context. Altogether, the tuple $(\Setup,\Prove,\Verify,\SimSetup,
\Sim,\Extract)$ needs to meet the following properties:

@@

As studied in \cite{cl06}, simulation-extractable NIZKPoKs formalize the concept
of ``signatures of knowledge'' (see, e.g., \cite{cs97}). Which basically means
that, given an $(\NIZKx,\NIZKw)$ pair from an NP relation, we can treat \NIZKx
as a public key, and \NIZKw as its corresponding private key, and leverage them
to build digital signature schemes -- with the advantage of being able to do so
while proving arbitrary claims, as long as they can be represented as an NP
relation. We note that, given a simulation-extractable NIZK system, it is
straightforward to build a signature of knowledge by adding the message to be
signed in the statement of the NIZK.

@@

\begin{description}
\item[$\SBCMparm \gets \SBCMSetup(\SBCMsecpar)$.] It produces public parameters
  for the other algorithms, given an input security parameter \SBCMsecpar.
\item[$(\SBCMvk,\SBCMsk) \gets \SBCMKeyGen(\SBCMparm)$.] Generates a
  verification-signing key pair.
\item[$(\SBCMcom,\pi,r) \gets \SBCMBlind(\SBCMvk,\osmsg,\smsg)$.] A user
  computes commitment \SBCMcom to request a signature over messages \osmsg (in
  committed form) and \smsg (in plain form), to signer with verification key
  \SBCMvk. The output is the commitment \SBCMcom, the randomness $r$ used to
  compute it, and a proof $\pi$ proving knowledge of \osmsg and \smsg in
  \SBCMcom.
\item[$\SBCMbsig \gets \SBCMSign(\SBCMsk,\SBCMcom,\pi,\smsg)$.] The
  signer, with signing key \SBCMsk, produces a blind signature \SBCMbsig over
  the messages commited to in commitment \SBCMcom, as well as the messages in
  \smsg, with associated proof $\pi$.
\item[$\SBCMsig \gets \SBCMUnblind(\SBCMvk,\SBCMbsig,\SBCMcom,r,\osmsg,\smsg)$.]
  A user, who requested a signature over \osmsg and \smsg, where \SBCMcom is a
  commitment over \osmsg using randomness $r$, finalizes the signature,
  computing \SBCMsig from the signer's partial signature \SBCMbsig.
\item[$1/0 \gets \SBCMVerify(\SBCMvk,\SBCMsig,\osmsg,\smsg)$.] Checks
  whether \SBCMsig is a valid signature over the set of messages \osmsg and
  \smsg, under verification key \SBCMvk.
\end{description}

@@

\paragraph{Augmented NIZKs.} %
Constructions of \SBCM (e.g. \cite{asm06}), as well as the formalization we just
described, require that the user proves, in zero-knowledge (via a NIZK),
knowledge of the messages to be signed in committed
form -- and the blinding factor used to hide them. Note that, in such
constructions, it is easy to extend their NIZK so that, instead of simply
proving knowledge of the messages signed in committed form, the party running
\SBCMBlind proves, in zero knowledge, some arbitrary claim over the messages to
be signed (both those in committed or plaintext form). This can be done by
extending the initial NIZK into a more general one. 
%
It is direct that, if the base \SBCM scheme satisfies blindness, then extending
it with an arbitrary zero-knowledge NIZK proof over the signed messages, still
maintains blindness (the adversary cannot distinguish which committed message
set is signed, in the blindness game).
%
We use this extension in our \CUASGen construction. Note that, under this
extension, we may also need to provide extra information to the \SBCMBlind,
\SBCMSign and \SBCMUnblind algorithms, as part of the extended statement being
proven, and new witnesses (even though some may not be part of the messages to
be signed). To make this explicit, we use the following notation to denote
that we use a NIZK for relation $\NIZKRel$, with values $x'$ and $w'$ that are
part of the statement being proven, but are not contained within the actual
\smsg or \osmsg:

@@

Next, we give an instantiation of an \SBCM scheme, based on BBS+ signatures.
We emphasize again that this is essentially equivalent to the protocol for
signing committed block of messages in \cite{asm06} and, also, to the equivalent
ones in \cite{cl02,ps16} (although not for BBS+ signatures). The main difference
being that we allow merging committed blocks of messages and blocks of
(plaintext) messages into the same signature.
%
Note also that, in our instantiation, we just include a generic \NIZK, for some
relation over witness $\overline{\smsg}$ (i.e., the messages to be blindly
signed), and statement $(\Ccom,\smsg)$ (i.e., their block commitment, and the
plainly signed messages). This is intentional, as we want to support cases where
proving arbitrary predicates is possible (as opposed to ``just'' proving that
the commitment is over the messages in $\overline{\smsg}$).
%
When we want to make explicit the relation over which the employed \NIZK is
defined, we add a $\NIZKRel$ superscript to the algorithms.

>>>>

\begin{description}
\item[$\Eparm \gets \ESetup(\Esecpar)$.] Produces public parameters \Eparm given
  a security parameter \Esecpar.
\item[$(\Eek,\Edk) \gets \EKeyGen(\Eparm)$.] Given public parameters \Eparm,
  produces an encryption-decryption key pair $(\Eek,\Edk)$.
\item[$\Ec \gets \EEnc(\Eek,\msg)$.] Encrypts message \msg with encryption key
  \Eek, producing ciphertext \Ec.
\item[$\msg \gets \EDec(\Edk,\Ec)$.] Decrypts ciphertext \Ec with decryption key
  \Edk.
\end{description}

@@

Let \NIZKRel be an NP relation defined by pairs of elements $(\NIZKx,\NIZKw)$,
where \NIZKx is a statement and \NIZKw a witness proving that $(\NIZKx,\NIZKw)
\in \NIZKRel$. For concrete relations, we write $\NIZKRel = \lbrace (\NIZKx),
(\NIZKw): f(x,w) \rbrace$, where $f(x,w)$ is a Boolean predicate denoting the
concrete conditions that \NIZKx and \NIZKw need to meet. The set of all \NIZKx
such that there exists a \NIZKw for which $(\NIZKx,\NIZKw) \in \NIZKRel$ is the
language, or \NIZKLang, for \NIZKRel. $\NIZKx \notin \NIZKLang$ means that
there is no $\NIZKw$ such that $(\NIZKx,\NIZKw) \in \NIZKRel$.

@@

When we want to make explicit the NP relation \NIZKRel to which the previous
algorithms refer to, we use $\NIZKSetup^\NIZKRel,\NIZKProve^\NIZKRel$, 
$\NIZKVerify^\NIZKRel$, etc., and omit the \NIZK prefix and super-index when
clear from context. Altogether, the tuple $(\Setup,\Prove,\Verify,\SimSetup,
\Sim,\Extract)$ needs to meet the following properties:

@@

As studied in \cite{cl06}, simulation-extractable NIZKPoKs formalise the concept
of ``signatures of knowledge'' (see, e.g., \cite{cs97}). Which basically means
that, given an $(\NIZKx,\NIZKw)$ pair from an NP relation, we can treat \NIZKx
as a public key, and \NIZKw as its corresponding private key, and leverage them
to build digital signature schemes -- with the advantage of being able to do so
while proving arbitrary claims, as long as they can be represented as an NP
relation. We note that, given a simulation-extractable NIZK system, it is
straightforward to build a signature of knowledge by adding the message to be
signed in the statement of the NIZK.

@@

\begin{description}
\item[$\SBCMparm \gets \SBCMSetup(\SBCMsecpar)$.] It produces public parameters
  for the other algorithms, given an input security parameter \SBCMsecpar.
\item[$(\SBCMvk,\SBCMsk) \gets \SBCMKeyGen(\SBCMparm)$.] Generates a
  verification-signing key pair.
\item[$(\SBCMcom,\pi,r) \gets \SBCMBlind(\SBCMvk,\osmsg,\smsg)$.] A user
  computes commitment \SBCMcom to request a signature over messages \osmsg (in
  committed form) and \smsg (in plain form), to signer with verification key
  \SBCMvk. The output is the commitment \SBCMcom, the randomness $r$ used to
  compute it, and a proof $\pi$ proving knowledge of \osmsg and \smsg in
  \SBCMcom.
\item[$\SBCMbsig \gets \SBCMSign(\SBCMsk,\SBCMcom,\pi,\smsg)$.] The
  signer, with signing key \SBCMsk, produces a blind signature \SBCMbsig over
  the messages committed to in commitment \SBCMcom, as well as the messages in
  \smsg, with associated proof $\pi$.
\item[$\SBCMsig \gets \SBCMUnblind(\SBCMvk,\SBCMbsig,\SBCMcom,r,\osmsg,\smsg)$.]
  A user, who requested a signature over \osmsg and \smsg, where \SBCMcom is a
  commitment over \osmsg using randomness $r$, finalises the signature,
  computing \SBCMsig from the signer's partial signature \SBCMbsig.
\item[$1/0 \gets \SBCMVerify(\SBCMvk,\SBCMsig,\osmsg,\smsg)$.] Checks
  whether \SBCMsig is a valid signature over the set of messages \osmsg and
  \smsg, under verification key \SBCMvk.
\end{description}

@@

\paragraph{Augmented NIZKs.} %
Constructions of \SBCM (e.g. \cite{asm06}), as well as the formalisation we just
described, require that the user proves, in zero-knowledge (via a NIZK),
knowledge of the messages to be signed in committed
form -- and the blinding factor used to hide them. Note that, in such
constructions, it is easy to extend their NIZK so that, instead of simply
proving knowledge of the messages signed in committed form, the party running
\SBCMBlind proves, in zero knowledge, some arbitrary claim over the messages to
be signed (both those in committed or plaintext form). This can be done by
extending the initial NIZK into a more general one. 
%
It is direct that, if the base \SBCM scheme satisfies blindness, then extending
it with an arbitrary zero-knowledge NIZK proof over the signed messages, still
maintains blindness (the adversary cannot distinguish which committed message
set is signed, in the blindness game).
%
We use this extension in our \CUASGen construction. Note that, under this
extension, we may also need to provide extra information to the \SBCMBlind,
\SBCMSign and \SBCMUnblind algorithms, as part of the extended statement being
proven, and new witnesses (even though some may not be part of the messages to
be signed). To make this explicit, we use the following notation to denote
that we use a NIZK for relation $\NIZKRel$, with values $x'$ and $w'$ that are
part of the statement being proven, but are not contained within the actual
\smsg or \osmsg:

@@

Next, we give an instantiation of an \SBCM scheme, based on BBS+ signatures.
We emphasise again that this is essentially equivalent to the protocol for
signing committed block of messages in \cite{asm06} and, also, to the equivalent
ones in \cite{cl02,ps16} (although not for BBS+ signatures). The main difference
being that we allow merging committed blocks of messages and blocks of
(plaintext) messages into the same signature.
%
Note also that, in our instantiation, we just include a generic \NIZK, for some
relation over witness $\overline{\smsg}$ (i.e., the messages to be blindly
signed), and statement $(\Ccom,\smsg)$ (i.e., their block commitment, and the
plainly signed messages). This is intentional, as we want to support cases where
proving arbitrary predicates is possible (as opposed to ``just'' proving that
the commitment is over the messages in $\overline{\smsg}$).
%
When we want to make explicit the relation over which the employed \NIZK is
defined, we add a $\NIZKRel$ superscript to the algorithms.

### 2022-10-04 prism-backend/research/gsac/app-related-extra.tex
Spellchecked full paper.

\begin{description}
\item[$(\gpk,\isk,\osk) \gets KeyGen(1^\secpar,\finsp)$.] Runs exactly as in
  \CUASGS, except that it now receives an opening function, which must be of
  the type $\finsp^{\smsg}$, for some \smsg.
\item[$(\upk,\usk) \gets UKG(1^\secpar)$.] Like in \CUASGS.  
\item[$\langle \cred,\utrans \rangle \gets
  \langle\Obtain(\usk,\ipk),\Issue(\isk,\upk)\rangle$.] Like in \CUASGS.
\item[$\sig \gets \Sign(\gpk,\cred,\msg)$.] Like in \CUASGS.
\item[$1/0 \gets \Verify(\gpk,\sig,\msg)$.] Like in \CUASGS.
\item[$(\upk,\pi) \gets \Open(\gpk,\osk,\trans,\sig,\msg)$.] Like in
  \CUASGS.
\item[$1/0 \gets \Judge(\gpk,\pi,\upk,\sig,\msg)$.] Like in \CUASGen. Note that
  \gpk includes an \opk with an opening fuction of type $\finsp^{\smsg}$.
\end{description}

@@

There are some differences, though. On the one hand, our signature anonymity
property is somehow in the middle of MPS's privacy-1 and privacy-2 variants.
Their privacy-1 variant is the traditional anonymity property of group
signatures, in which the opener is honest and the adversary can call the opening
oracle except for challenge signatures. In their privacy-2 variant, the opener
is fully corrupt (i.e., \adv~ receives \osk), but the adversary can only be
challenged with signatures that produce the same \yinsp value ($G_{j_b}(id_b)$
in MPS). In our \UAS model, we allow the adversary to corrupt openers at will
(getting ther \osk), but the challenge signatures must have been generated using
the key of an uncorrupted opener; still, \adv~can call the open oracle for
challenge signatures, as long as they have the same \yinsp value. We believe
that these differences are mostly of theoretical interest, though. In practice,
what matters is that any variant of \feval and \finsp functions ($F$ and $G_j$
in MPS) that has too much granularity in their ranges, will lead to a barely
private system. This is a known issue, for instance, in functional encryption
\cite{bsw11}.

On the other hand, anonymous issuance and the capability to customize issuance
policies are unachievable by MPS. Anonymous issuance simply does not make sense
in MPS, as it only supports one credential (without attributes) per user, and
customized issuance is achieved in \UAS via the \fissue functions, with no
equivalent in MPS -- instead, MPS can be seen as having the fixed policy of
``proving knowledge of a user secret key''. These extensions are not trivial
from a modelling point of view, and also have a big impact in the practicality
of the resulting system. Also, MPS does not include verifiable openings. While
this is easy to add, we consider it to be essential, given that the proposed
generalization of opening allows the opener to output ``any value''. Hence, the
need to ensure that the produced value is the legitimate one seems to be more
necessary than ever. Finally, our \feval function is a generalization of $F$ in
MPS, as it allows two outputs: one will be returned in the clear along with the
signature, and the other will be encrypted. Indeed, making part of the output
unencrypted allows implementing very useful variants such as anonymous
credentials with selective disclosure, as shown before.

@@

Finally, note that, in MPS, $G$ is further parameterized with a value $j$, which
essentially is the result of applying $F$ to the message and signer identity,
and is not leaked to the opener nor any other third party. The equivalent in
\UAS is the $\yeval^1$ value which, in \CUASGen, is encrypted with a single-use
key pair, and is an input of \finsp.

@@

\begin{proof}
  Given an adversary \adv~against unforgeability-1 of \CUASMPS, as defined in
  the MPS model, we build \advB that breaks signature unforgeability of the
  underyling \CUASGen, as defined for \UAS.

@@

\begin{proof}
  Given an adversary \adv~against unforgeability-2 of \CUASMPS, as defined in
  the MPS model, we build \advB that breaks non-frameability of the underyling
  \CUASGen, as defined for \UAS.

@@

\subsubsection{\CUASRAC Construction.} %
Briefly, this is achieved via a $(\fissue^1,\feval^{\dattrs,H,V,L},
\finsp^{F})$-\CUASGenInt restriction, where $\fissue^1$ is as in
\figref{fig:func-restrictions}, and $\feval^{\dattrs,H,V,L}$ and $\finsp^{H}$
are ase specified in \esref{eq:funcs-rac}.

@@

\begin{proof}
  Given \adv~ against signature anonymity of \CUASDAC as defined in
  $\Exp^{sig-anon-b}_{\adv,dac}(1^\secpar)$, we build an adversary \advB against
  signature anonymity of \CUASGenInt.
  %
  \adv's oracles are simulated as in the proof for issuance anonymity of
  \CUASDAC -- in this case, \adv's \oracle{SigLoR} oracle corresonds to \advB's
  \CHALb. Again, the simulation is perfect, and whenever \adv~wins its
  $\Exp^{sig-anon-b}$ game, so does \advB.
  % 
  \qed
\end{proof}

>>>>

\begin{description}
\item[$(\gpk,\isk,\osk) \gets KeyGen(1^\secpar,\finsp)$.] Runs exactly as in
  \CUASGS, except that it now receives an opening function, which must be of
  the type $\finsp^{\smsg}$, for some \smsg.
\item[$(\upk,\usk) \gets UKG(1^\secpar)$.] Like in \CUASGS.  
\item[$\langle \cred,\utrans \rangle \gets
  \langle\Obtain(\usk,\ipk),\Issue(\isk,\upk)\rangle$.] Like in \CUASGS.
\item[$\sig \gets \Sign(\gpk,\cred,\msg)$.] Like in \CUASGS.
\item[$1/0 \gets \Verify(\gpk,\sig,\msg)$.] Like in \CUASGS.
\item[$(\upk,\pi) \gets \Open(\gpk,\osk,\trans,\sig,\msg)$.] Like in
  \CUASGS.
\item[$1/0 \gets \Judge(\gpk,\pi,\upk,\sig,\msg)$.] Like in \CUASGen. Note that
  \gpk includes an \opk with an opening function of type $\finsp^{\smsg}$.
\end{description}

@@

There are some differences, though. On the one hand, our signature anonymity
property is somehow in the middle of MPS's privacy-1 and privacy-2 variants.
Their privacy-1 variant is the traditional anonymity property of group
signatures, in which the opener is honest and the adversary can call the opening
oracle except for challenge signatures. In their privacy-2 variant, the opener
is fully corrupt (i.e., \adv~ receives \osk), but the adversary can only be
challenged with signatures that produce the same \yinsp value ($G_{j_b}(id_b)$
in MPS). In our \UAS model, we allow the adversary to corrupt openers at will
(getting their \osk), but the challenge signatures must have been generated using
the key of an uncorrupted opener; still, \adv~can call the open oracle for
challenge signatures, as long as they have the same \yinsp value. We believe
that these differences are mostly of theoretical interest, though. In practice,
what matters is that any variant of \feval and \finsp functions ($F$ and $G_j$
in MPS) that has too much granularity in their ranges, will lead to a barely
private system. This is a known issue, for instance, in functional encryption
\cite{bsw11}.

On the other hand, anonymous issuance and the capability to customise issuance
policies are unachievable by MPS. Anonymous issuance simply does not make sense
in MPS, as it only supports one credential (without attributes) per user, and
customised issuance is achieved in \UAS via the \fissue functions, with no
equivalent in MPS -- instead, MPS can be seen as having the fixed policy of
``proving knowledge of a user secret key''. These extensions are not trivial
from a modelling point of view, and also have a big impact in the practicality
of the resulting system. Also, MPS does not include verifiable openings. While
this is easy to add, we consider it to be essential, given that the proposed
generalisation of opening allows the opener to output ``any value''. Hence, the
need to ensure that the produced value is the legitimate one seems to be more
necessary than ever. Finally, our \feval function is a generalisation of $F$ in
MPS, as it allows two outputs: one will be returned in the clear along with the
signature, and the other will be encrypted. Indeed, making part of the output
unencrypted allows implementing very useful variants such as anonymous
credentials with selective disclosure, as shown before.

@@

Finally, note that, in MPS, $G$ is further parameterised with a value $j$, which
essentially is the result of applying $F$ to the message and signer identity,
and is not leaked to the opener nor any other third party. The equivalent in
\UAS is the $\yeval^1$ value which, in \CUASGen, is encrypted with a single-use
key pair, and is an input of \finsp.

@@

\begin{proof}
  Given an adversary \adv~against unforgeability-1 of \CUASMPS, as defined in
  the MPS model, we build \advB that breaks signature unforgeability of the
  underlying \CUASGen, as defined for \UAS.

@@

\begin{proof}
  Given an adversary \adv~against unforgeability-2 of \CUASMPS, as defined in
  the MPS model, we build \advB that breaks non-frameability of the underlying
  \CUASGen, as defined for \UAS.

@@

\subsubsection{\CUASRAC Construction.} %
Briefly, this is achieved via a $(\fissue^1,\feval^{\dattrs,H,V,L},
\finsp^{F})$-\CUASGenInt restriction, where $\fissue^1$ is as in
\figref{fig:func-restrictions}, and $\feval^{\dattrs,H,V,L}$ and $\finsp^{H}$
are as specified in \esref{eq:funcs-rac}.

@@

\begin{proof}
  Given \adv~ against signature anonymity of \CUASDAC as defined in
  $\Exp^{sig-anon-b}_{\adv,dac}(1^\secpar)$, we build an adversary \advB against
  signature anonymity of \CUASGenInt.
  %
  \adv's oracles are simulated as in the proof for issuance anonymity of
  \CUASDAC -- in this case, \adv's \oracle{SigLoR} oracle corresponds to \advB's
  \CHALb. Again, the simulation is perfect, and whenever \adv~wins its
  $\Exp^{sig-anon-b}$ game, so does \advB.
  % 
  \qed
\end{proof}

### 2022-10-04 prism-backend/research/gsac/app-uas-proofs.tex
Spellchecked full paper.

\begin{proof}[\thmref{thm:issue-anonymity-uas}; Issuance anonymity of \CUASGen]
  We prove the special case in which the adversary makes only one query to the
  \OBTCHALb oracle. The generalization to polynomially many queries follows
  from a standard hybrid argument.

@@

  In this proof, we restrict to the case in which the adversary can only make
  one query to the challenge oracle. Note however that the generalization to
  polynomially many queries given in \cite{bsz05} applies here too (with the
  corresponding security loss). Thus, proving security for one query to the
  challenge oracle is enough.

@@

  \paragraph{(c) The output of \finsp matches the output of \Open.} %
  After (a), and correctness of the public key encryption algorihtm, the \yinsp
  value output by \Open is the correct decryption of
  \cinsp. After (c), the $(\yeval^0=\yeval,\yeval^1)$ values output by
  \ExtractSign match the evaluation of \feval. Thus, simulation extractability
  of $\NIZK^{\Sign}$ ensures that $\finsp((\yeval^0,\yeval^1),\upk,\lbrace
  (\cid_i,\attrs_i)\rbrace_{i\in[n]},\msg) = \yinsp$ and, also, that \yinsp
  matches the $\yinsp'$ value extracted by \ExtractSign. Thus, the probability
  of \adv~winning at line 13 is negligible due to simulation extractability
  of $\NIZK^{\Sign}$.

@@

\paragraph{Signature Anonymity.} To see why the interactive variant has
signature anonymity, assume an adversary \adv~that breaks it. We build \advB
against the non-interactive \ExpSigAnonb from \adv~as follows. \advB initializes
everything as in the \ExpSigAnonb game. When \adv~initiates a call to its
interactive \SIGN (resp. \CHALb) oracle, \advB forwards it to its own oracle
(but concatenating the random number to the message to be signed). \advB
forwards the response from its oracle to \adv. After such simulation, \advB just
outputs whatever $\adv$ outputs. Clearly, the simulation is perfect and, if
\adv~wins with non-negligible probability in the interactive case, then so
does \advB in the non-interactive case. Specifically, note that, since the \Sign
algorithm is probabilistic, even if a malicious verifier picks the same random
number in several queries (to the same or different users), the result will be
indistinguishable with overwhelming probability.

>>>>

\begin{proof}[\thmref{thm:issue-anonymity-uas}; Issuance anonymity of \CUASGen]
  We prove the special case in which the adversary makes only one query to the
  \OBTCHALb oracle. The generalisation to polynomially many queries follows
  from a standard hybrid argument.

@@

  In this proof, we restrict to the case in which the adversary can only make
  one query to the challenge oracle. Note however that the generalisation to
  polynomially many queries given in \cite{bsz05} applies here too (with the
  corresponding security loss). Thus, proving security for one query to the
  challenge oracle is enough.

@@

  \paragraph{(c) The output of \finsp matches the output of \Open.} %
  After (a), and correctness of the public key encryption algorithm, the \yinsp
  value output by \Open is the correct decryption of
  \cinsp. After (c), the $(\yeval^0=\yeval,\yeval^1)$ values output by
  \ExtractSign match the evaluation of \feval. Thus, simulation extractability
  of $\NIZK^{\Sign}$ ensures that $\finsp((\yeval^0,\yeval^1),\upk,\lbrace
  (\cid_i,\attrs_i)\rbrace_{i\in[n]},\msg) = \yinsp$ and, also, that \yinsp
  matches the $\yinsp'$ value extracted by \ExtractSign. Thus, the probability
  of \adv~winning at line 13 is negligible due to simulation extractability
  of $\NIZK^{\Sign}$.

@@

\paragraph{Signature Anonymity.} To see why the interactive variant has
signature anonymity, assume an adversary \adv~that breaks it. We build \advB
against the non-interactive \ExpSigAnonb from \adv~as follows. \advB initialises
everything as in the \ExpSigAnonb game. When \adv~initiates a call to its
interactive \SIGN (resp. \CHALb) oracle, \advB forwards it to its own oracle
(but concatenating the random number to the message to be signed). \advB
forwards the response from its oracle to \adv. After such simulation, \advB just
outputs whatever $\adv$ outputs. Clearly, the simulation is perfect and, if
\adv~wins with non-negligible probability in the interactive case, then so
does \advB in the non-interactive case. Specifically, note that, since the \Sign
algorithm is probabilistic, even if a malicious verifier picks the same random
number in several queries (to the same or different users), the result will be
indistinguishable with overwhelming probability.

### 2022-10-04 prism-backend/research/gsac/conclusion-paper.tex
Spellchecked full paper.

We present a general model for privacy-preserving signatures and authentication,
and provide a generic construction, secure in our model, that allows
different privacy-vs-utility tradeoffs to be reached.
%
Then, we prove that well-known schemes are special cases of our generic
construction. The implied schemes include group signatures, anonymous
credentials (with and without revocation), ring signatures, or the recently
proposed multimodal private signatures.

@@

For future work, an obvious line is to come up with (and implement) concrete
instantiations of our generic construction in order to evaluate efficiency in
real-world use cases. Alternative generic constructions are also of interest --
for instance, based on structure-preserving signatures.
%
Finally, in this work we focus only on utility over \emph{one} signature. But
extending our model and constructions to span utility over \emph{multiple}
signatures promises to be interesting, both regarding its modelling, the
potential use cases, and the generalization capabilities.

>>>>

We present a general model for privacy-preserving signatures and authentication,
and provide a generic construction, secure in our model, that allows
different privacy-vs-utility trade-offs to be reached.
%
Then, we prove that well-known schemes are special cases of our generic
construction. The implied schemes include group signatures, anonymous
credentials (with and without revocation), ring signatures, or the recently
proposed multimodal private signatures.

@@

For future work, an obvious line is to come up with (and implement) concrete
instantiations of our generic construction in order to evaluate efficiency in
real-world use cases. Alternative generic constructions are also of interest --
for instance, based on structure-preserving signatures.
%
Finally, in this work we focus only on utility over \emph{one} signature. But
extending our model and constructions to span utility over \emph{multiple}
signatures promises to be interesting, both regarding its modelling, the
potential use cases, and the generalisation capabilities.
